---
title: "step6_real_analysis"
output: html_document
date: "2025-03-14"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(AnVIL)
library(ggplot2)
library(reshape2)
library(dplyr)
library(readr)
library("recount3")
library("limma")
library("SummarizedExperiment")  # assays function come from here
source("GEDE_data_prep.R")
source("GEDE_simulation.R")
source("GEDE_real_analysis.R")
library(pheatmap)
library(DESeq2)
library(Matrix)
library(GEDE)
library(edgeR)
library(xgboost)
library(randomForest)
library(Hmisc)
library(VennDiagram)
library(eulerr)
library(patchwork)
library(biomaRt)

# for pathway enrichment
# library(clusterProfiler)
# library(org.Hs.eg.db)  # For human genes (change for other species)
# library(enrichplot)  # For visualization
# library(ReactomePA)  # Reactome pathway enrichment

# change output dir
out_dir = "/home/sliu/github/GEDE_benchmark/output/real_data_analysis"
knitr::opts_knit$set(root.dir = out_dir)

```


# Data prep
### 1.1a, Prep RNA data
```{r 1.1a.prep_RNA_data, eval = FALSE, message = FALSE}
# use recount3 and recover raw counts

# download data from recount3
all_projects <- available_projects()
selected_proj = subset(all_projects, organism=="human" & project_home == "data_sources/tcga")
selected_proj <- selected_proj[selected_proj$n_samples>500, ]
selected_vars = c("tcga.gdc_cases.demographic.race", "tcga.gdc_cases.demographic.gender", "tcga.gdc_cases.diagnoses.tumor_stage", "tcga.gdc_cases.exposures.cigarettes_per_day")

### still use the BRCA data, this
Data_BRCA = pull_recount3_data(available_project = selected_proj, keyword="BRCA", group_vector = selected_vars)
group = Data_BRCA$group
counts = Data_BRCA$counts

# downsample race: white 900 -> 300, and only keep 200 black
table(Data_BRCA$group$tcga.gdc_cases.demographic.race)
# use %in% instead of == to get rid of NA when facing NA == sth (returns NA)
black_samples = row.names(group[group$tcga.gdc_cases.demographic.race %in% c("black or african american"), ])
white_samples = row.names(group[group$tcga.gdc_cases.demographic.race %in% c("white"), ])
# subsample white to 300
set.seed(1234)
white_samples <- sample(white_samples, 300)
final_samples <- c(white_samples, black_samples)
# new data
downsampled_counts <- counts[, final_samples]
downsampled_group <- group[final_samples, ]
dim(downsampled_counts)
dim(downsampled_group)

Data_BRCA$group <- downsampled_group
Data_BRCA$counts <- downsampled_counts
rm(counts, group, downsampled_group, downsampled_counts)
table(Data_BRCA$group$tcga.gdc_cases.demographic.race)

# make sure samples are in the same order in count and metadata table
sum(colnames(Data_BRCA$counts) == rownames(Data_BRCA$group)) == dim(Data_BRCA$group)[1]

# save data for future usage
save(Data_BRCA, file="input_Recount3_BRCA_race.Rdata")
```

### 1.1b, Prep Protein data


# Analysis before GEDE
### 2.0, load variables here for analysis
```{r load_variable, message=FALSE}
# considering that we may switch data, put all variables here for global management

# the variable names might be different, here is Data_BRCA
load("input_Recount3_BRCA_race.Rdata")
input_data <- Data_BRCA
deg_condition = "tcga.gdc_cases.demographic.race"
cutoff_pvalue = 0.05
cutoff_log2fc = 1


```


### 2.1, run DEG
########## call DESeq2, edgeR, and limma to run DEG, Keep intersection (as GT) + union (to check extra genes identified by GEDE)
```{r 2.1_call_DEG_for_ground_truth_on_full_data, message=FALSE}
############ Get DEGs for the full data
# DESeq2
deg_deseq2 <- run_DESeq2_for_df_and_meta(df_count=input_data$counts, df_meta=input_data$group, single_condition=deg_condition)

# limma needs a voom transformed data
deg_limma <- run_limma_for_df_and_meta(df_count=input_data$counts, df_meta=input_data$group, single_condition=deg_condition)

# edgeR
deg_edger <- run_edgeR_for_df_and_meta(df_count=input_data$counts, df_meta=input_data$group, single_condition=deg_condition)



# while the number is too high, let's increase log2fc to 1~2 and then check the overlap and make a van di plot
filtered_deseq2 <- filter_deg(deg_deseq2, log2fc=cutoff_log2fc)
print(dim(filtered_deseq2))
filtered_limma <- filter_deg(deg_limma, log2fc = cutoff_log2fc)
print(dim(filtered_limma))
filtered_edger <- filter_deg(deg_edger, log2fc = cutoff_log2fc)
print(dim(filtered_edger))

# regular Venn
compare_deg_non_proportional_figure(rownames(filtered_deseq2), rownames(filtered_limma), rownames(filtered_edger))

# proportional Venn
compare_deg_proportional_figure(rownames(filtered_deseq2), rownames(filtered_limma), rownames(filtered_edger))

# based on RNA-seq data results, limm results is much smaller than the other 2, so I will use DESeq2+EdgeR overlap/union but ignore limma
out6 = list()
out6$deg_all_records_deseq2 <- deg_deseq2
out6$deg_all_records_limma <- deg_limma
out6$deg_all_records_edger <- deg_edger

out6$deg_sig_deseq2 <- filtered_deseq2
out6$deg_sig_limma <- filtered_limma
out6$deg_sig_edger <- filtered_edger


out6$union_deg <- union(rownames(filtered_deseq2), rownames(filtered_edger))  # this is the finding before data correction
out6$overlap_deg <- intersect(rownames(filtered_deseq2), rownames(filtered_edger)) # this serves as ground truth finding

save(out6, file="output_real_data_analysis.Rdata")

```


### 2.2, subsample saturation for DEG before GEDE
########## Downsample every 10%
```{r 2.2_saturation_analysis_of_DEG_before_GEDE, message=FALSE}
df_meta <- input_data$group
group_values = levels(as.factor(df_meta[[deg_condition]]))
# split group and do random sample
sample_grp_1 = rownames(df_meta[df_meta[deg_condition] == group_values[1], ])
sample_grp_2 = rownames(df_meta[df_meta[deg_condition] == group_values[2], ])

# loop DEGs by different sample rate, note that for the 200 vs 300 RNA-seq case, 20% can recover 87.5% DEGs
# Note: here we count DEG recovery rate: those found in full data, NOT all DEGs here
sample_raio = seq(0.1, 0.9, 0.1)

# init saturation results 
saturation_union_recover_rate = c()
saturation_intersect_recover_rate = c()

for (raio in sample_raio) {
  print(raio)
  # random sample 
  set.seed(123)
  select_1 = sample(sample_grp_1, size = round(raio * length(sample_grp_1)))
  select_2 = sample(sample_grp_2, size = round(raio * length(sample_grp_2)))
  keep_data = c(select_1, select_2)
  
  # filter df and metadata
  temp_df_count = input_data$counts[ , keep_data]
  temp_df_meta = input_data$group[keep_data, ]
  
  # call DEG, note we use "new_log2fc=1" here because we scale up the DEGs form full data

  temp_deg_deseq2 <- run_DESeq2_for_df_and_meta(df_count=temp_df_count, df_meta=temp_df_meta, single_condition=deg_condition)
  temp_deg_deseq2 <- filter_deg(temp_deg_deseq2, log2fc=cutoff_log2fc)
  
  temp_deg_edger <- run_edgeR_for_df_and_meta(df_count=temp_df_count, df_meta=temp_df_meta, single_condition=deg_condition)
  temp_deg_edger <- filter_deg(temp_deg_edger, log2fc=cutoff_log2fc)
  
  # create a new list to store results and nest it into out6
  temp_list = list()
  temp_list$deg_deseq2 = temp_deg_deseq2
  temp_list$deg_edger = temp_deg_edger
  temp_list$union_deg = union(rownames(temp_deg_deseq2), rownames(temp_deg_edger))
  temp_list$intersect_deg = intersect(rownames(temp_deg_deseq2), rownames(temp_deg_edger))
  temp_list$gt_recover_by_union = intersect(temp_list$union_deg, out6$overlap_deg)
  temp_list$gt_recover_by_union_ratio = length(temp_list$gt_recover_by_union) / length(out6$overlap_deg)
  temp_list$gt_recover_by_intersect = intersect(temp_list$intersect_deg, out6$overlap_deg)
  temp_list$gt_recover_by_intersect_ratio = length(temp_list$gt_recover_by_intersect) / length(out6$overlap_deg)
  
  # add plot stats
  saturation_union_recover_rate = c(saturation_union_recover_rate, temp_list$gt_recover_by_union_ratio)
  saturation_intersect_recover_rate = c(saturation_intersect_recover_rate, temp_list$gt_recover_by_intersect_ratio)
  
  # add this list to out6
  out6[[paste0("subsample_result_before_GEDE_ratio_", raio)]] <- temp_list
  rm(temp_list)
}

# save and plot results
saturation_results = list()
saturation_results$ratio = sample_raio
saturation_results$union_recover = saturation_union_recover_rate
saturation_results$intersect_recover = saturation_intersect_recover_rate

out6$saturation_before_GEDE = saturation_results
rm(saturation_results)

# save results
save(out6, file="output_real_data_analysis.Rdata")


# generate line plots
df <- data.frame(
  ratio = out6$saturation_before_GEDE$ratio,
  union_recover = out6$saturation_before_GEDE$union_recover,
  intersect_recover = out6$saturation_before_GEDE$intersect_recover
)

df_long <- melt(df, id.vars = "ratio", variable.name = "Type", value.name = "Recovery")

# Create line plot
ggplot(df_long, aes(x = ratio, y = Recovery, color = Type, group = Type)) +
  geom_line(size = 1) +  # Draw lines
  geom_point(size = 2) + # Add points for better visibility
  geom_text(aes(label = round(Recovery, 3)), vjust = -0.5, size = 4) + # Add text labels
  labs(title = "Saturation Analysis", x = "Subsample ratio", y = "Recovery ratio") +
  scale_color_manual(values = c("red", "blue")) +  # Customize colors
  theme_minimal()


```




# Analysis after GEDE
### 3.0 apply GEDE on log transformed data
```{r 3.0_apply_GEDE_polish, eval = FALSE, message=FALSE}
load("input_Recount3_BRCA_race.Rdata")
input_data <- Data_BRCA

condition_variable = "tcga.gdc_cases.demographic.race"

# prep data for GEDE
df_count = input_data$counts
df_meta = input_data$group
temp_metadata <- df_meta[colnames(df_count), , drop = TRUE]  # Reorder to match count data
# this is group vector
temp_group <- factor(temp_metadata[[deg_condition]])
levels(temp_group) <- gsub(" ", "_", levels(temp_group))  # replace space by _ for the limma contrast
# numeric for GEDE input
numeric_group <- as.numeric(temp_group) - 1


# GEDE needs transposed input: gene * sample
transpose_df_count <- transpose(df_count)
# Restore row and column names
rownames(transpose_df_count) <- colnames(df_count)  # Old column names → new row names
colnames(transpose_df_count) <- rownames(df_count)  # Old row names → new column names


# log2 transformation: GEDE need log data because it assumes multi-normal dist
log_df = log2(transpose_df_count+1)
normality_results <- apply(log_df, 2, function(x) {
  if (length(unique(x)) > 1) {  # Ensure column is not constant
    return(shapiro.test(x)$p.value)
  } 
})
normality_results <- unlist(normality_results)

# make some qq plots for columns: pick from normality test results
selected_columns <- c("ENSG00000162777.16", "ENSG00000143106.12", "ENSG00000031698.12")
column_name <- "ENSG00000162777.16"

# Create QQ plot using ggplot2
ggplot(log_df, aes(sample = .data[[column_name]])) +
  stat_qq() + 
  stat_qq_line() +
  labs(title = paste("QQ Plot for", column_name), x = "Theoretical Quantiles", y = "Sample Quantiles") +
  theme_minimal()



# run gede based on log df and then transfer it back
gede_output <- GEDE(log_df, X=numeric_group, K.method="vprop", HD=TRUE)

# check output (transpose back)
new_df = transpose(gede_output$Ystar)
rownames(new_df) <- colnames(gede_output$Ystar)  # Old column names → new row names
colnames(new_df) <- rownames(gede_output$Ystar)  # Old row names → new column names

# transfer back to count by 2**x
new_count_df = round(pmax(2^new_df-1, 0))


# change of depth (colsums)
old_depth = colsums(df_count)
new_depth = colsums(new_count_df)
new_ratio = new_depth / old_depth
hist(new_ratio, 
     breaks = 100,  # Number of bins
     col = "blue",  # Color of bars
     border = "black",  # Edge color
     main = "Histogram of depth ratios", 
     xlab = "Ratio", 
     xlim = c(0,2),
     ylab = "Frequency")

# folder changes before/after GEDE
old_means <- sapply(unique(numeric_group), function(g) {
  rowMeans(df_count[, numeric_group == g, drop = FALSE])  # Compute mean for each row within the group
})
old_fc <- old_means[,1]  / (old_means[,2]+1)

new_means <- sapply(unique(numeric_group), function(g) {
  rowMeans(new_count_df[, numeric_group == g, drop = FALSE]) 
})
new_fc <- new_means[,1] / (new_means[,2]+1)


# plot differences
plot_old_fc = old_fc
plot_new_fc = new_fc
# make plot
plot_old_fc[plot_old_fc > 10] <- 10
plot_old_fc[plot_old_fc < -10] <- -10
plot_new_fc[plot_new_fc > 10] <- 10
plot_new_fc[plot_new_fc < -10] <- -10
# Combine into a dataframe for boxplot
df <- data.frame(
  FoldChange = c(plot_old_fc, plot_new_fc),
  Group = rep(c("Old FC", "New FC"), each = length(plot_old_fc))
)
medians <- tapply(df$FoldChange, df$Group, median)
# Create boxplot
boxplot(FoldChange ~ Group, data = df, 
        main = "Comparison of Old and New Fold Change (Clipped at ±10)", 
        ylab = "Fold Change",
        col = c("lightblue", "lightgreen"),  # Box colors
        border = "black",                    # Outline color
        notch = TRUE)                         # Notched boxplot for median confidence


# save results
input_data$gede_counts <- new_count_df
Data_BRCA <- input_data
all(sum(rownames(Data_BRCA$group)  == colnames(Data_BRCA$gede_counts)))
save(Data_BRCA, file="input_Recount3_BRCA_race.Rdata")

```



### 3.1, full data DEG after GEDE
```{r 3.1_call_DEG_on_full_data_after_GEDE, message=FALSE}
# need to reload data as we added new things
load("input_Recount3_BRCA_race.Rdata")
input_data <- Data_BRCA
# load previous results
load("output_real_data_analysis.Rdata")



############ Get DEGs for the full data
# DESeq2
deg_deseq2 <- run_DESeq2_for_df_and_meta(df_count=input_data$gede_counts, df_meta=input_data$group, single_condition=deg_condition, pvalue=cutoff_pvalue, log2fc=cutoff_log2fc)

# limma needs a voom transformed data
deg_limma <- run_limma_for_df_and_meta(df_count=input_data$gede_counts, df_meta=input_data$group, single_condition=deg_condition, pvalue=cutoff_pvalue, log2fc=cutoff_log2fc)

# edgeR
deg_edger <- run_edgeR_for_df_and_meta(df_count=input_data$gede_counts, df_meta=input_data$group, single_condition=deg_condition, pvalue=cutoff_pvalue, log2fc=cutoff_log2fc)



# while the number is too high, let's increase log2fc to 1~2 and then check the overlap and make a van di plot
filtered_deseq2 <- filter_deg(deg_deseq2, log2fc= cutoff_log2fc)
print(dim(filtered_deseq2))
filtered_limma <- filter_deg(deg_limma, log2fc = cutoff_log2fc)
print(dim(filtered_limma))
filtered_edger <- filter_deg(deg_edger, log2fc = cutoff_log2fc)
print(dim(filtered_edger))

# regular Venn
compare_deg_non_proportional_figure(rownames(filtered_deseq2), rownames(filtered_limma), rownames(filtered_edger))

# proportional Venn
compare_deg_proportional_figure(rownames(filtered_deseq2), rownames(filtered_limma), rownames(filtered_edger))

# add to results
out6$deg_gede_records_deseq2 <- deg_deseq2
out6$deg_gede_records_limma <- deg_limma
out6$deg_gede_records_edger <- deg_edger
out6$deg_sig_gede_deseq2 <- filtered_deseq2
out6$deg_sig_gede_limma <- filtered_limma
out6$deg_sig_gede_edger <- filtered_edger

out6$union_gede_deg <- union(rownames(filtered_deseq2), rownames(filtered_edger))   # no limma here for consistency
out6$overlap_gede_deg <- intersect(rownames(filtered_deseq2), rownames(filtered_edger)) 

# gede DEG recover and overlap 
out6$gede_union_recover_ratio = length(intersect(out6$union_gede_deg, out6$overlap_deg)) / length(out6$overlap_deg)
out6$gede_overlap_recover_ratio = length(intersect(out6$overlap_gede_deg, out6$overlap_deg)) / length(out6$overlap_deg)
out6$gede_extra_genes = setdiff(out6$overlap_gede_deg, out6$overlap_deg)

save(out6, file="output_real_data_analysis.Rdata")

```



### 3.2, saturation analysis after GEDE
```{r 3.2_saturation_analysis_after_GEDE, message=FALSE}
group_values = levels(as.factor(df_meta[[deg_condition]]))
# split group and do random sample
sample_grp_1 = rownames(df_meta[df_meta[deg_condition] == group_values[1], ])
sample_grp_2 = rownames(df_meta[df_meta[deg_condition] == group_values[2], ])

# loop DEGs by different sample rate, note that for the 200 vs 300 RNA-seq case, 20% can recover 87.5% DEGs
# Note: here we count DEG recovery rate: those found in full data, NOT all DEGs here
sample_raio = seq(0.1, 0.9, 0.1)

# init saturation results 
saturation_union_recover_rate = c()
saturation_intersect_recover_rate = c()

for (ratio in sample_raio) {
  print(ratio)
  # random sample 
  set.seed(123)
  select_1 = sample(sample_grp_1, size = round(ratio * length(sample_grp_1)))
  select_2 = sample(sample_grp_2, size = round(ratio * length(sample_grp_2)))
  keep_data = c(select_1, select_2)
  
  # filter df and metadata (here is the data after GEDE)
  temp_df_count = input_data$gede_counts[ , keep_data]
  temp_df_meta = input_data$group[keep_data, ]
  
  # call DEG, note we use "new_log2fc=1" here because we scale up the DEGs form full data

  temp_deg_deseq2 <- run_DESeq2_for_df_and_meta(df_count=temp_df_count, df_meta=temp_df_meta, single_condition=deg_condition, pvalue=cutoff_pvalue, log2fc= new_log2fc)
  temp_deg_deseq2 <- filter_deg(temp_deg_deseq2, log2fc= cutoff_log2fc)
  
  temp_deg_edger <- run_edgeR_for_df_and_meta(df_count=temp_df_count, df_meta=temp_df_meta, single_condition=deg_condition, pvalue=cutoff_pvalue, log2fc= new_log2fc)
  temp_deg_edger <- filter_deg(temp_deg_edger, log2fc= cutoff_log2fc)
  
  # create a new list to store results and nest it into out6
  temp_list = list()
  temp_list$deg_deseq2 = temp_deg_deseq2
  temp_list$deg_edger = temp_deg_edger
  temp_list$union_deg = union(rownames(temp_deg_deseq2), rownames(temp_deg_edger))
  temp_list$intersect_deg = intersect(rownames(temp_deg_deseq2), rownames(temp_deg_edger))
  temp_list$gt_recover_by_union = intersect(temp_list$union_deg, out6$overlap_deg)
  temp_list$gt_recover_by_union_ratio = length(temp_list$gt_recover_by_union) / length(out6$overlap_deg)
  temp_list$gt_recover_by_intersect = intersect(temp_list$intersect_deg, out6$overlap_deg)
  temp_list$gt_recover_by_intersect_ratio = length(temp_list$gt_recover_by_intersect) / length(out6$overlap_deg)
  
  # add plot stats
  saturation_union_recover_rate = c(saturation_union_recover_rate, temp_list$gt_recover_by_union_ratio)
  saturation_intersect_recover_rate = c(saturation_intersect_recover_rate, temp_list$gt_recover_by_intersect_ratio)
  
  # add this list to out6
  out6[[paste0("subsample_result_after_GEDE_ratio_", ratio)]] <- temp_list
  rm(temp_list)
}

# save and plot results
saturation_results = list()
saturation_results$ratio = sample_raio
saturation_results$union_recover = saturation_union_recover_rate
saturation_results$intersect_recover = saturation_intersect_recover_rate

out6$saturation_after_GEDE = saturation_results
rm(saturation_results)



# save results
save(out6, file="output_real_data_analysis.Rdata")


# generate line plots
df <- data.frame(
  ratio = out6$saturation_after_GEDE$ratio,
  union_recover = out6$saturation_after_GEDE$union_recover,
  intersect_recover = out6$saturation_after_GEDE$intersect_recover
)

df_long <- melt(df, id.vars = "ratio", variable.name = "Type", value.name = "Recovery")

# Create line plot
ggplot(df_long, aes(x = ratio, y = Recovery, color = Type, group = Type)) +
  geom_line(size = 1) +  # Draw lines
  geom_point(size = 2) + # Add points for better visibility
  geom_text(aes(label = round(Recovery, 3)), vjust = -0.5, size = 4) + # Add text labels
  labs(title = "Saturation Analysis", x = "Subsample ratio", y = "Recovery ratio") +
  scale_color_manual(values = c("red", "blue")) +  # Customize colors
  theme_minimal()




# let's plot 2 saturations together
df_sat_overlap <- data.frame(
  ratio = out6$saturation_after_GEDE$ratio,
  raw_data = out6$saturation_before_GEDE$intersect_recover,
  gede_data = out6$saturation_after_GEDE$intersect_recover
)
df_long_overlap <- melt(df_sat_overlap, id.vars = "ratio", variable.name = "Type", value.name = "Recovery")


df_sat_union <- data.frame(
  ratio = out6$saturation_after_GEDE$ratio,
  raw_data = out6$saturation_before_GEDE$union_recover,
  gede_data = out6$saturation_after_GEDE$union_recover
)
df_long_union <- melt(df_sat_union, id.vars = "ratio", variable.name = "Type", value.name = "Recovery")

# plot them together
p1 <- ggplot(df_long_overlap, aes(x = ratio, y = Recovery, color = Type, group = Type)) +
  geom_line(size = 1) +  # Draw lines
  geom_point(size = 2) + # Add points for better visibility
  geom_text(aes(label = round(Recovery, 3)), vjust = -0.5, size = 4) + # Add text labels
  labs(title = "Saturation Analysis", x = "Subsample ratio", y = "Recovery ratio by OVERLAP DEGs") +
  ylim(0, 1) +
  scale_color_manual(values = c("red", "blue")) +  # Customize colors
  theme_minimal()

p2 <- ggplot(df_long_union, aes(x = ratio, y = Recovery, color = Type, group = Type)) +
  geom_line(size = 1) +  # Draw lines
  geom_point(size = 2) + # Add points for better visibility
  geom_text(aes(label = round(Recovery, 3)), vjust = -0.5, size = 4) + # Add text labels
  labs(title = "Saturation Analysis", x = "Subsample ratio", y = "Recovery ratio by UNION DEGs") +
  ylim(0, 1) +
  scale_color_manual(values = c("red", "blue")) +  # Customize colors
  theme_minimal()

p1 + p2

# Save the figure as a file
combined_plot <- p1 + p2
ggsave(filename = "saturation_analysis.png", plot = combined_plot, width = 15, height = 6, dpi = 300)

```



# check differences
### Why genes are not DEG in subsample
```{r 4.1_check_non_DEGs, message=FALSE}
extra_DEG_in_raw <- setdiff(out6$overlap_deg, out6$union_gede_deg)

temp_record_deseq2 <- out6$deg_gede_records_deseq2[rownames(out6$deg_gede_records_deseq2) %in% extra_DEG_in_raw, ]

# print results out
sum(temp_record_deseq2$padj > 0.05)   # 67
sum(abs(temp_record_deseq2$log2FoldChange) < 1) # 519
temp_abs_log2fc <- abs(temp_record_deseq2$log2FoldChange)

hist(temp_abs_log2fc, 
     breaks = 10,  # Number of bins
     col = "blue",  # Color of bars
     border = "black",  # Edge color
     main = "Histogram of abs log2fc", 
     xlab = "Ratio", 
     xlim = c(0,1),
     ylab = "Frequency")

```



### Extra findings in GEDE: do they make sense
```{r 4.2_extra_DEGs_from_GEDE, message=FALSE}
# extra genes
temp_extra = out6$gede_extra_genes

# Remove version numbers (everything after the dot)
temp_extra_clean <- sub("\\..*", "", temp_extra)

# Query Ensembl to get gene names
# those related with cancer: CEACAM6, MUC4, CYP19A1, GATA4
gene_mapping <- getBM(
  attributes = c("ensembl_gene_id", "external_gene_name"),
  filters = "ensembl_gene_id",
  values = temp_extra_clean,
  mart = useMart("ensembl", dataset = "hsapiens_gene_ensembl")
)

# run pathway enrichment

load("input_Recount3_BRCA_race.Rdata")
input_data <- Data_BRCA
```


# End





